---
title: "Applied Spatial Data Analysis with R"
subtitle: "Chapter 2 : Classes for Spatial Data in R"
output: html_notebook
---

# Introduction
This Notebook is rough document where I have written all the codes that I found interesting and experimented upon. This notebook is more like a digital record and may turn out to be rough patches of codes in the future.

# Packages
```{r Packages list, message=FALSE, warning=FALSE, include=FALSE}
# Clearing the variables list
rm(list = ls())

# loading required packages
library(sp)
```



# 01-15-2022
```{r}
getClass("CRS")
```

Building a simple Spatial object from a bounding box matrix, and a missing coordinate reference system:
```{r}
m <- matrix(c(0,0,1,1), ncol = 2, dimnames = list(NULL, c("min", "max")))

crs <- CRS(projargs = as.character(NA))

crs

S <- Spatial(bbox = m, proj4string = crs)
S
```
 
 
 SpatialPoints
 
```{r}
CRAN_df <- read.table("datasets/CRAN051001a.txt", header = TRUE)
CRAN_mat <- cbind(CRAN_df$long, CRAN_df$lat)
row.names(CRAN_mat) <- 1:nrow(CRAN_mat)
str(CRAN_mat)
```
 
```{r}
getClass("SpatialPoints")
```

# 01-22-2022

## methods
```{r}
llCRS <- CRS("+proj=longlat +ellps=WGS84")
CRAN_sp <- SpatialPoints(CRAN_mat, proj4string = llCRS)
summary(CRAN_sp)
bbox(CRAN_sp)
```

## SpatialPointsDataFrame
```{r}
CRAN_spdf1 <- SpatialPointsDataFrame(CRAN_mat,CRAN_df, proj4string = llCRS, match.ID = T)
CRAN_spdf1[4,]
```

## SpatialLines
```{r}
library(maps)
japan <- map("world", "japan", plot = TRUE)
p4s <- CRS("+proj=longlat +ellps=WGS84")
library(maptools)
SLjapan <- map2SpatialLines(japan, proj4string = p4s)
str(SLjapan, max.level = 2)
```






















